Scale Space Edge Detection

### 2018-03-05 paper.tex
updates

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

\section{Edge Detection}
    Detecting edges in images has long been a problem with many uniques solutions to approach it. Generally speaking, the majority of algorithms are usually checking the image for some of the following features:

@@

    where

    \begin{equation}
        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} + 4f_{0,0}
    \end{equation}
    \begin{equation}
        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} + 4f_{0,0}
    \end{equation}

>>>>

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}

@@

\section{Edge Detection Background}
    Detecting edges in images has long been a problem with many uniques solutions to approach it. Generally speaking, the majority of algorithms are usually checking the image for some of the following features:

@@

    where $\gamma \in [0,1]$ is a hyperparameter and,

    \begin{equation}
        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} - 4f_{0,0}
    \end{equation}
    \begin{equation}
        (\nabla^2_\times f)_{0,0} = \frac{1}{2}(f_{-1,-1} + f_{-1,+1} + f_{+1,-1} + f_{+1,+1} - 4f_{0,0})
    \end{equation}

    Note that $f_{-1,1}$ represents $f(x-1, y+1)$. Now that we have defined what discrete scale spaces and their derivatives look like, we can start to define what an edge is.

\section{Defining an Edge in Scale Space}
    We classify edge points as points which have gradient magnitueds that assume a maximum in the direction of the gradient. Let us denote the magnitude of the gradient of $L$ as $L_g$. Then we define an edge in the scale space with the following conditions

    \begin{equation} \label{eq:c1}
        \begin{aligned}
            L_{gg} &= 0 \\ 
            L_{ggg} &< 0
        \end{aligned}
    \end{equation}

    The way we can then represent these conditions in terms of spatial derivatives is as follows

    \begin{equation}
        \begin{aligned}
            L_{gg} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
            L_{ggg} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
        \end{aligned}
    \end{equation}

    This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$. Thus this adds two more conditions that must be satisified for an edge to be classified in the scale space.

    \begin{equation} \label{eq:c2}
        \begin{aligned}
            \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
            \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
        \end{aligned}
    \end{equation}

    Then equation \ref{eq:c1} in conjunction with \ref{eq:c2} form the neccessary constraints for us to define an edge in the scale space. Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.

    The approach we took was to let our edge strength meteric be defined by the gradient magnitude that has been normalized by our $\gamma$ factor. In this case we can define it as

    \begin{equation}
        \begin{aligned}
            G_{\gamma}L &= L_{g,\gamma}^2 \\
            &= t^{\gamma}(L_x^2+L_y^2)
        \end{aligned}
    \end{equation}
